
% \textbf{After resigning from Nanjing Huawei}, I contacted with my advisor in
% Nanjing University, Dr.\ Enyi Tang, and joined his research group
% in optimizing floating point arithmetic.
% I was responsible for developing an automatic tool to analyze
% the potential vulnerable calculation with fixed floating points,
% then replace the fixed floating points with the arbitrary precision
% floating points.
% This work was published on the ICSE 2019.

% This work is based on the
% \href{http://rosecompiler.org/ROSE_HTML_Reference/index.html}{Rose Compiler}
% and \href{https://github.com/klee/klee}{KLEE}.
% The tool is publicly available at my
% \href{https://github.com/whj0401/numopt_preprocess}{repository},
% and our paper was published on the ICSE 2019.

% \smallskip
% \textbf{During my Ph.D. study}, my research focused on \textbf{binary code similarity
% analysis (BCSA)} and its application.
% My advisor, Dr. Shuai Wang, and I cooperated with Tencent Keen Lab
% in this topic.

During my Ph.D. study, my research focused on \textbf{binary code similarity
analysis (BCSA)} and its application.
My advisor, Dr. Shuai Wang, and I cooperated with Tencent Keen Lab
in this topic.

\smallskip
\textit{What is BCSA?}~
Industrial developers often use machine-learning-based BCSA to analyze
software without source code, such as malware and commercial software.
BCSA tools work like a search engine for binary code. Given a query binary
code piece, BCSA returns several most similar binary code pieces in the
database. The similarity is measured by the semantic information extracted
from the binary code. However, analyzing binary code is difficult due to
lack of human-readable symbols, complicated optimized code, and even
obfuscated code.

\begin{itemize}
    \item To improve the precision of machine-learning-based BCSA, we proposed
    to use the semantic information extracted by the under-constrained
    symbolic execution (USE). This work was published on the TSE 2022.

    \item To enhance BCSA's capability of understanding binary code semantics,
    we design \texttt{sem2vec} to directly embed the semantic information,
    extracted by USE,
    which shows a significant improvement in understanding
    obfuscated binary code. This work was published on the TOSEM 2023.

    \item We also investigate a promising application of BCSA, binary software
    composition analysis (Binary SCA). We evaluated the state-of-the-art BCSA tools
    on the binary SCA task and proposed several enhancements. This work was
    published on the Euro S\&P 2024.

    % \item We also notice the privacy issue of software composition analysis (SCA) and
    % build the first privacy-preserving SCA framework. We just got a revision from
    % ICSE 2025.
\end{itemize}

Our team is also investigating enhancing software security with LLMs. For instance,
reducing false positives of static analysis tools, improving decompilers, etc.
