See full publications on my homepage (\href{https://whj0401.github.io/}{https://whj0401.github.io/}).
\begin{enumerate}
    \item Wai Kin Wong, Daoyuan Wu, \textbf{Huaijin Wang}, Zongjie Li, Zhibo Liu, Shuai Wang, Qiyi Tang, Sen Nie, Shi Wu.
    ``DecLLM: LLM-Augmented Recompilable Decompilation for Enabling Programmatic Use of Decompiled Code.''
    In \textit{ACM SIGSOFT International Symposium on Software Testing and Analysis (ISSTA)}. 2025.
    \item \textbf{Huaijin Wang}, Zhibo Liu, Yanbo Dai, Shuai Wang, Qiyi Tang, Sen Nie, and Shi Wu.
    ``Preserving Privacy in Software Composition Analysis: A Study of Technical Solutions and Enhancements.''
    In \textit{the IEEE/ACM 47th International Conference on Software Engineering (ICSE)}. 2025.
    \item \textbf{Huaijin Wang}, Zhibo Liu, Ying Wang, Shuai Wang, Qiyi Tang, Sen Nie, and Shi Wu.
    ``Are We There Yet? Filling the Gap Between ML-Based Binary Similarity Analysis and Binary Software Composition Analysis.''
    In \textit{the IEEE European Symposium on Security and Privacy (Euro S\&P)}. 2024.
    
    % \item Zhaoyu Wang, Pingchuan Ma, \textbf{Huaijin Wang}, Shuai Wang.
    % ``PP-CSA: Practical Privacy-Preserving Software Call Stack Analysis.''
    % In \textit{ACM Conference on Object-Oriented Programming, Systems, Languages, and Applications (OOPSLA)}. 2024.
    
    \item WONG, Wai Kin, \textbf{Huaijin Wang*}, Zongjie Li, and Shuai Wang.
    ``BinAug: Enhancing Binary Similarity Analysis with Low-Cost Input Repairing''.
    In \textit{IEEE/ACM 46st International Conference on Software Engineering (ICSE)}. 2024.
    
    % \item Wei Chen, \textbf{Huaijin Wang}, Weixi Gu, and Shuai Wang.
    % ``RLTrace: Synthesizing High-Quality System Call Traces for OS Fuzz Testing.''
    % In \textit{International Conference on Information Securit (ISC)}. 2023.

    \item \textbf{Huaijin Wang}, Pingchuan Ma, Shuai Wang, Qiyi Tang, Sen Nie, and Shi Wu.
    ``“sem2vec: Semantics-Aware Assembly Tracelet Embedding.''
    In \textit{ACM Transactions on Software Engineering and Methodology (TOSEM)}. 2023.
    
    \item Zongjie Li, Pingchuan Ma, \textbf{Huaijin Wang}, Shuai Wang, Qiyi Tang, Sen Nie, and Shi Wu.
    ``Unleashing the Power of Compiler
    Intermediate Representation to Enhance Neural Program Embeddings.''
    In \textit{IEEE/ACM 44st International Conference on Software Engineering (ICSE)}. 2022.
    
    \item \textbf{Huaijin Wang}, Pingchuan Ma, Yuanyuan Yuan, Zhibo Liu, Shuai Wang, Qiyi Tang, Sen Nie, and Shi Wu.
    ``Enhancing DNN-Based
    Binary Code Function Search With Low-Cost Equivalence Checking.''
    In \textit{IEEE Transactions on Software Engineering (TSE)}. 2022.
    
    % \item Wong, Wai Kin, \textbf{Huaijin Wang}, Pingchuan Ma, Shuai Wang, Mingyue Jiang, Tsong Yueh Chen, Qiyi Tang, Sen Nie, and Shi Wu.
    % ``Deceiving Deep Neural Networks-Based Binary Code Matching with Adversarial Programs.''
    % In \textit{IEEE International
    % Conference on Software Maintenance and Evolution (ICSME)}. 2022.
    
    \item \textbf{Huaijin Wang}, Shuai Wang, Dongpeng Xu, Xiangyu Zhang, and Xiao Liu.
    ``Generating Effective Software Obfuscation Sequences with Reinforcement Learning.''
    In \textit{IEEE Transactions on Dependable and Secure Computing (TDSC)}. 2020.
    
    % \item Xie Wang, \textbf{Huaijin Wang}, Zhendong Su, Enyi Tang, Xin Chen, Weijun Shen, Zhenyu Chen, Linzhang Wang, Xianpei Zhang, and Xuandong Li.
    % ``Global optimization of numerical programs via prioritized stochastic algebraic transformations.''
    % In \textit{IEEE/ACM 41st
    % International Conference on Software Engineering (ICSE)}. 2019.
\end{enumerate}
